### 2018-07-03 doc/plos/text/manuscript.tex
add fusion subsection

>>>>

\subsection*{Fusion}

The fitting procedure described above gives a disparate set of predictions of
wILI for various locations in the US. We combine---via sensor fusion
\cite{farrow2016modeling}---all available predictions into a single, unified
nowcast of wILI throughout the US.

Sensor fusion is a generalization of the Kalman filter \cite{kalman1960new}
which relaxes assumptions regarding the process being tracked---the
distribution of wILI in this case. In particular, sensor fusion describes the
combination of a set of measurements without requiring a linear Markov process
model. This combination is optimal in a least-squares sense when the
measurements are unbiased with normally distributed error.

For nowcasting flu, this means practically that the fusion inputs should be in
the same units and on the same scale as wILI and should have normally
distributed error. By applying the fitting procedure above, we meet the first
requirement, and the assumption that errors are normally distributed is
generally not grossly violated.

Nowcasting is conceptually a two-step process. First, measurements are fused to
give an estimate of latent system state (namely, wILI in US states and
territories). Second, nowcasts for each location of interest (namely, wILI in
the US as a whole, HHS regions, census divisions, states, and territories) are
extracted as a linear combination of latent state wILI.

More concretely, given a vector of ``sensor`` readings (surveillance values as
described above) $z$, we apply the sensor fusion kernel to produce a vector
nowcast $y$.

\begin{align*}
A &= (H^T R^{-1} H)^{-1} H^T R^{-1} \\
x &= A z \\
y &= W x
\end{align*}

Elements of $z$ are the sensor reading of a particular data source in a
particular location, and elements of $y$ are a unified nowcast in each location
of interest.

Matrices $H$ and $W$ are mappings from latent state-space to measurement-space
and output-space respectively. Matrix $R$ is the empirical covariance of sensor
noise, where noise is defined as the difference between sensor readings and
ground truth measured on historical data. Intermediate matrix $A$ conceptually
represents the optimal translation from measurement-space to latent
state-space, given the reverse mapping ($H$) and sensor noise covariance ($R$).

$H$ and $W$ are defined by the geographical makeup and population distribution
within the US; they are constants, modulo changes in population over long
periods of time (e.g. years). On any given week, sensors $z$ are given by
surveillance data, and covariance $R$ is estimated based on historical data.
